Uncertainty-aware graph-based multimodal remote sensing classification

### 2021-07-06 latex/CEUR/paper.tex
Removed equals sign alignment and rearranged expression so that equation number at RHS wasn't pushed out of line.

\subsection{Subjective Logic}
Before describing how a model which can produce subjective opinions as its output can be trained, it is first important to understand what these opinions can be constructed.
Subjective Logic (SL), takes an evidence-based approach to decision making \cite{Josang2016}.
Expressing an opinion using measured quantities of belief allows the distinction to be made between uncertainty due to a lack of evidence (vacuity) and uncertainty due to the presence of conflicting evidence (dissonance).
A multinomial opinion, $\omega$, can be expressed as $\omega=\left(\mathbf{b}, u, \mathbf{a}\right)$, where $\mathbf{b}$ is a belief mass vector, the scalar $u$ is the uncertainty mass and $\mathbf{a}$ is the base rate vector.
For an output, $\mathbf{y}$, of dimension K
\begin{equation}
    \mathbf{b}\in\mathbb{R}^K,\quad\mathbf{a}\in\mathbb{R}^K,\quad\mathbf{y}\in\mathbb{R}^K.
\end{equation}
A projection of $\omega$ onto a probability distribution can be made according to
\begin{equation}
    P(y=k) = b_k + a_ku.
\label{eq:prob_projection}
\end{equation}
Given that for the base rate vector $\sum_{k=1}^Ka_k=1$, an additivity requirement is described by
\begin{equation}
    u+\sum_{k=1}^K b_k=1.
\end{equation}

@@

\subsection{Subjective models}
In order to obtain models which will give node-level Dirichlet distribution parameters, the softmax output activation function used in a GCN is substituted for a ReLU function.
In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the K-dimensional concentration parameters of the $\text{i}^\text{th}$ node.
In order to train an evidential model, the loss function is made up of two components; a squared error term which is minimised in order to classify a greater proportion of the nodes correctly and a variance term which is minimized to incentivize the model to provide confident predictions where possible.
This loss, $\mathcal{L}(\boldsymbol{\theta})$, is given by
\begin{equation}
\begin{split}
    \mathcal{L}(\boldsymbol{\theta})&=\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\text{Var}(p_{ik})\right],\\
    &=\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\frac{\left(\frac{\alpha_{ik}}{S_i}\right)\left(1-\frac{\alpha_{ik}}{S_i}\right)}{S_i-K}\right],
\end{split}
\label{eq:core_loss}
\end{equation}
where $i\in\mathbb{L}$ refers to the fact that the loss is computed using a sum only over nodes in the training set, $\mathbb{L}$.
Models trained with such an output activation and loss function will be denoted using the `S-' prefix in order to indicate they provide subjective predictions, e.g. S-GCN.

>>>>

\subsection{Subjective Logic}
Subjective Logic (SL), takes an evidence-based approach to decision making \cite{Josang2016}.
Expressing an opinion using measured quantities of belief allows the distinction to be made between uncertainty due to a lack of evidence (vacuity) and uncertainty due to the presence of conflicting evidence (dissonance).
A multinomial opinion, $\omega$, can be expressed as $\omega=\left(\mathbf{b}, u, \mathbf{a}\right)$, where $\mathbf{b}$ is a belief mass vector, the scalar $u$ is the uncertainty mass and $\mathbf{a}$ is the base rate vector.
For an output, $\mathbf{y}$, of dimension K
\begin{equation}
    \mathbf{b}\in\mathbb{R}^K,\quad\mathbf{a}\in\mathbb{R}^K,\quad\mathbf{y}\in\mathbb{R}^K.
\end{equation}
A projection of $\omega$ onto a probability distribution can be made according to
\begin{equation}
    P(y=k) = b_k + a_ku.
\label{eq:prob_projection}
\end{equation}
Given that for the base rate vector $\sum_{k=1}^Ka_k=1$, an additivity requirement is described by
\begin{equation}
    u+\sum_{k=1}^K b_k=1.
\end{equation}

@@

\subsection{Subjective models}
In order to obtain models which will give node-level Dirichlet distribution parameters, the softmax output activation function used in a GCN is substituted for a ReLU function.
In this way, the model is trained to output non-negative evidence contributions, $\mathbf{E}\in\mathbb{R}^{N\times K}$, where $\mathbf{E}_{i} = \boldsymbol{\alpha}_{i}-\mathbf{1}$ and $\boldsymbol{\alpha}_{i}$ refers to the K-dimensional concentration parameters of the $\text{i}^\text{th}$ node.
In order to train an evidential model, the loss function is made up of two components; a squared error term which is minimised in order to classify a greater proportion of the nodes correctly and a variance term which is minimized to incentivize the model to provide confident predictions where possible.
This loss, $\mathcal{L}(\boldsymbol{\theta})$, is given by
\begin{equation}
\begin{split}
    \mathcal{L}(\boldsymbol{\theta})=\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\text{Var}(p_{ik})\right],\\
    =\sum_{i\in\mathbb{L}}\sum_k \left[(p_{ik}-y_{ik})^2+\frac{\alpha_{ik}}{S_i^2}\left(\frac{S_i-\alpha_{ik}}{S_i-K}\right)\right],
\end{split}
\label{eq:core_loss}
\end{equation}
where $i\in\mathbb{L}$ refers to the fact that the loss is computed using a sum only over nodes in the training set, $\mathbb{L}$.
Models trained with such an output activation and loss function will be denoted using the `S-' prefix in order to indicate they provide subjective predictions, e.g. S-GCN.
